\documentclass[review, authoryear]{elsarticle}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{enumitem}   
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{plain}
\newtheorem{lem}[thm]{\protect\lemmaname}
\providecommand{\lemmaname}{Lemma}
\providecommand{\theoremname}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem*{remark}{Remark}
%\usepackage[margin=1.5in]{geometry}
\usepackage{geometry}

%% <remove "preprint submitted to elsevier">
%% \makeatletter
%% \def\ps@pprintTitle{%
%% \let\@oddhead\@empty
%% \let\@evenhead\@empty
%% \def\@oddfoot{}%
%% \let\@evenfoot\@oddfoot}
%% \makeatother
%% </remove "preprint submitted to elsevier">

\begin{document}
\begin{frontmatter}
\title{There is no uniformly unbiased independence test for densities}
\author{Jonas Moss}
\ead{jonasmgj@math.uio.no}
\address{Department of Mathematics, University of Oslo, PB 1053, Blindern, NO-0316, Oslo, Norway}
\begin{abstract} 
There is no uniformly unbiased independence test for densities. 
\end{abstract}
\end{frontmatter}

\begin{definition}
A family $\mathcal{I}$ is \emph{separating} if it contains a collection of nicely shrinking sets to $x$ for almost every $x \in \mathbb{R}^k$.
\end{definition}


\begin{thm}
\label{lem:Main theorem}
Let $\mathcal{I}$ be a separating family of sets. Assume that
(i) For all $I \in \mathcal{I}$ there is a pair $P\in \mathcal{P}$ and $Q \in \mathcal{Q}$ such that $P\mid_{I^c} = Q\mid_{I^c}$, 
(ii) the family $\mathcal{P}$ includes the uniform distribution on $I$ for all $I \in \mathcal{I}$. Then there is no uniformly unbiased test of $P$ against $Q$.
\end{thm}

\begin{remark}
Both (i) and (ii) can probably be weakened. For instance, (ii) could probably be weaked enough to accomodate unimodality. And it's probably possible to use some $\epsilon$s to make the support equal to $\mathbb{R}^k$.
\end{remark}

For example: $\mathcal{P}$ is the class of uniform distributions in $I$ while $\mathcal{Q}$ is the class of every other distribution defined on $I$.

Examples:
\begin{enumerate}
	\item Independence testing
	\item Conditional independence testing
	\item Symmetry: 
	\item Smoothness: Any kind of smoothness where $1$ is smooth.
	\item Unimodality: Maybe, if some extra conditions are used. 
	\item Goodness-of-fit testing: Obvious for uniform distributions. Try to make it work for e.g. the normal distribution. 
\end{enumerate}


Strong results:
\begin{enumerate}
	\item Independence testing
	\item Two
	\item Three
\end{enumerate}

Weaker results:
\begin{enumerate}
	\item Mean
	\item Most from Romano
	\item Conditional independence testing
\end{enumerate}


\bibliographystyle{elsarticle-harv}
\bibliography{power.bib}

\end{document}
